\documentclass[letterpaper,10pt]{article}

% Dependencies
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage[default]{sourcesanspro} % Sans-serif font

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Unicode
\input{glyphtounicode}
\pdfgentounicode=1

% Section Formatting
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Custom Commands
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Job Heading
\newcommand{\jobHeading}[3]{
  \noindent\textbf{#1} — #2 \hfill \textit{#3} \\
}

% Bullet List Environment
\newenvironment{resume_list}{
  \vspace{-6pt}
  \begin{itemize}[itemsep=2pt, leftmargin=18pt]
}{\end{itemize}}

\renewcommand\labelitemi{--}

% ---------------- Document ----------------

\begin{document}

\documentTitle{{Anmol Kumar}}{
    \href{tel:7838602045}{\raisebox{-0.15\height} \faMobile\ 7838602045} ~ | ~
    \href{mailto:anmolnoida09@gmail.com}{\raisebox{-0.15\height} \faEnvelope\ anmolnoida09@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/anmol-kumar-3b1323321/}{\raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/anmolkumar} ~ | ~
    \href{https://github.com/anmoldotkr}{\raisebox{-0.15\height} \faGithub\ github.com/anmoldotkr}
}

\section{Summary}
Results-oriented DevOps Engineer with 2+ years of experience specializing in AWS cloud infrastructure and CI/CD automation. Proficient in containerization using Docker and orchestrating pipelines with Jenkins and AWS CodePipeline. extensive experience in provisioning Infrastructure as Code (IaC) via CloudFormation and implementing Blue-Green deployment strategies to minimize downtime and streamline release cycles
\section{Technical Skills}
\begin{resume_list}
  \item \textbf{Cloud:} AWS (S3, Lambda, EC2, CloudWatch, API Gateway, Route53, DynamoDB, code-Pipeline, ECS Fargate, RDS)
  \item \textbf{DevOps:} Docker, smee.io, Nginx, Fluentd, Jenkins, Terraform, CloudFormation
  \item \textbf{Programming:} Python, Shell/Bash, Node.js
  \item \textbf{APIs \& Tools:} REST APIs, Postman, Git, Log Analysis, Debugging
  \item \textbf{Monitoring:} ElasticSearch, CloudWatch
  \item \textbf{Databases:} MySQL, MongoDB, DynamoDB
\end{resume_list}

\section{Professional Experience}


\jobHeading{Jr DevOps Engineer}{Impressico Business Solutions, Noida}{Aug 2024 – Present}
\begin{resume_list}
  \item Managed and automated AWS infrastructure using Infrastructure as Code (IaC) and Jenkins, provi-
sioning services including S3, CloudFront, ECS Fargate, ECR, Lambda, EC2, IAM, and VPC.
  \item Replaced manual AWS resource creation with automated, version-controlled CloudFormation templates and
CLI scripts, improving deployment speed, reliability, and consistency.
   \item Implemented automated start/stop of AWS RDS and ECS services on weekends to optimize costs, integrated
with Slack for real-time notifications.
  \item Integrated Jenkins pipelines with Bitbucket webhooks using smee.io, enabling real-time automated builds upon code commits and pull requests.
  \item Implemented Automated snapshot of Daily AMI Backup using Data Lifecycle Manager(DLM) service.
  \item Configured automated build triggers in AWS CodePipeline for branch-specific code pushes, integrated with
Slack notifications, reducing manual deployment efforts and improving CI/CD efficiency.
\end{resume_list}
\jobHeading{Software Engineering Intern}{Impressico Business Solutions, Noida}{Feb 2024 – Jul 2024}
\begin{resume_list}
  \item Created UI with React.js, integrating components with backend APIs to deliver seamless user experiences.
  \item Built REST APIs using Node.js (Express) for a microservices-based analytics tool.
  \item Deployed applications on AWS using EC2, S3, CloudWatch; configured Nginx for load balancing and high
availability.
\end{resume_list}

\section{Key Projects}
\begin{resume_list}
  \item A full-stack MERN application to manage books with CRUD, rating, and filter features. Deployed using Kubernetes and Minikube, with services containerized and orchestrated via YAML configurations. \href{https://github.com/anmoldotkr/BookApp}{\bfseries [GitHub]}
  \item Implemented CI/CD using CloudFormation; reduced deployment time from 30min to 6min. \href{https://github.com/anmoldotkr/ECS_CFT}{\bfseries [GitHub]}
  \item AI-powered code review tool built with Gemini API to analyze GitHub pull requests. 
Generates review comments using NLP, improves PR quality, and integrates with GitHub workflows. \href{https://github.com/anmoldotkr/Code-Reviewer}{\bfseries [GitHub]}
  \item CDN caching via CloudFront improved load speed by 65\%; reduced infra cost by 75\%.
\end{resume_list}

\section{Education}
\jobHeading{Bachelor of Application}{IIMT Group of Management}{2021 – 2024}
\begin{resume_list}
  \item CGPA: 6.8
\end{resume_list}

\section{Certifications \& Achievements}
\begin{resume_list}
  \item \textbf{Certifications:} Git \& GitHub, Data Structures (Coursera), Palo Alto Cybersecurity Foundation, CCNAv7
  \item \textbf{Achievements:} College Hackathon
\end{resume_list}

\end{document}
